---
title: '20190612'
output: ''
---

```{r}
gmailAddress <- c(
  "tim@gmail.com",
  "anita",
  "yellen@gmail.com",
  "huang@gmail.com"
)
```



```{r}
i <- 1
print(gmailAddress[[i]])

for(i in seq_along(gmailAddress)){
  print(gmailAddress[[i]])
}
```



```{r}
# ?}?l?]?w
gmailAddress <- c(
  "tim@gmail.com",
  "anita",
  "yellen@gmail.com",
  "huang@gmail.com"
)

cat("?_?l???p\n")
gmailAddress

# for loop
library(stringr)
for(i in seq_along(gmailAddress)){
  if(!str_detect(gmailAddress[[i]],"@gmail.com")){
    correctGmailAddress <-
      str_c(gmailAddress[[i]],"@gmail.com")
    gmailAddress[[i]] <- correctGmailAddress
  }
}

cat("?ץ??᪬?p\n")
gmailAddress
```


```{r}
load(url("https://www.dropbox.com/s/qnz9paigf61yjus/commitHistory.Rda?raw=1"))
```

```{r}
for(i in seq_along(commitHistory)){
  print(
    str_c(
      "Author is ",
      commitHistory[[i]][["commit"]][["author"]][["name"]],
      ". Committer is ",
      commitHistory[[i]][["commit"]][["committer"]][["name"]]
      )
    )
}
```

```{r}
for(i in seq_along(commitHistory)){
  print(commitHistory[[i]]$commit$author$name)
}
for(i in seq_along(commitHistory)){
  print(commitHistory[[i]]$commit$committer$name)
}
```


```{r}
i<-1

for(i in seq_along(commitHistory)){print(commitHistory[[i]]$commit$author$name)}

for(i in seq_along(commitHistory)){print(commitHistory[[i]]$commit$committer$name)}

for(i in seq_along(commitHistory)){print(commitHistory[[i]]$commit$committer$date)}
```



????0?Gprint?u?C?ӡvcommit??author????committer???޿??P?_???G?C

#sequence source
```{r}
commitHistory
```

#body
print?u??i?ӡvcommit??author????committer???޿??P?_???G?C
```{r}
i <- 1
(commitHistory[[i]][["commit"]][["author"]][["name"]]==commitHistory[[i]][["commit"]][["committer"]][["name"]]) -> logiResult
print(logiResult)
```

#for loop
```{r}
for(i in seq_along(commitHistory)){
  (commitHistory[[i]][["commit"]][["author"]][["name"]]==
     commitHistory[[i]][["commit"]][["committer"]][["name"]]) ->
    logiResult
  print(logiResult)  
}
```

?d??3
#???Ȥ@?G?s?U?ӨC??commit??author?C
```{r}
load(url("https://www.dropbox.com/s/qnz9paigf61yjus/commitHistory.Rda?raw=1"))
```

0. saving container
```{r}
saveCommitAuthor <-
  vector("character",length(commitHistory))
```

1. sequence source
```{r}
commitHistory
```

2. body
?s?U?ӡu??i?ӡvcommit??author?C
```{r}
i<- 1

commitHistory[[i]]$commit$author$name -> saveCommitAuthor[[i]]
```


?ˬd?@?U
```{r}
saveCommitAuthor
```

3. for loop
```{r}
saveCommitAuthor <-
  vector("character",length(commitHistory)) # 0.
for(i in seq_along(commitHistory)){
  commitHistory[[i]]$commit$author$name -> saveCommitAuthor[[i]]
}

saveCommitAuthor

```


#???ȤG?G?s?U?ӨC??commit??committer?C
0. saving container
```{r}
saveCommitcommitter<-
  vector("character",length(commitHistory))
```

1. sequence source
```{r}
commitHistory
```

2. body
?s?U?ӡu??i?ӡvcommit??committer?C

```{r}
i<- 1

commitHistory[[i]]$commit$committer$name -> saveCommitcommitter[[i]]
```

?ˬd?@?U
```{r}
saveCommitcommitter
```

3. for loop

```{r}
saveCommitcommitter <-
  vector("character",length(commitHistory)) # 0.

for(i in seq_along(commitHistory)){
  commitHistory[[i]]$commit$committer$name -> saveCommitcommitter[[i]]
}
saveCommitcommitter

```

#???ȤT?G?s?U?ӨC??author?Pcommitter?P?H??commitDate?C
0. saving container
```{r}
savecommitDate <-
  vector("character",length(commitHistory))
```

1. sequence source
```{r}
commitHistory
```

2. body
?s?U?ӡu??i?ӡvcommit??committer?C

```{r}
i<- 1
commitHistory[[i]]$commit$committer$name == saveCommitcommitter[[i]]
commitHistory[[i]]$commit$committer$date[commitHistory[[i]]$commit$committer$name == saveCommitcommitter[[i]]]->
```

?ˬd?@?U
```{r}
savecommitDate
```

#3 answer
???ȤT?G?s?U?ӨC??author?Pcommitter?P?H??commitDate?C

?L?????ȡG
?s?U?ӨC??commit??author, committer, commitDate.
?s?U?ӨC??commit??author==commiter?????G

0. saving container
saveEveryThing <- vector("list",length(commitHistory))
saveSameLogi <- vector("logical",length(commitHistory))
1. sequence source
commitHistory
2. body
i <- 1

author_i <- commitHistory[[i]]$commit$author$name
committer_i <- commitHistory[[i]]$commit$committer$name
commitDate_i <- commitHistory[[i]]$commit$committer$date

(author_i==committer_i) -> saveSameLogi[[i]]
list(
  author=author_i,
  committer=committer_i,
  commitDate=commitDate_i
) -> saveEveryThing[[i]]
?ˬd?@?U

saveEveryThing
saveSameLogi
3. for loop
saveEveryThing <- vector("list",length(commitHistory))
saveSameLogi <- vector("logical",length(commitHistory))
for(i in seq_along(commitHistory)){
  author_i <- commitHistory[[i]]$commit$author$name
  committer_i <- commitHistory[[i]]$commit$committer$name
  commitDate_i <- commitHistory[[i]]$commit$committer$date

  (author_i == committer_i) -> saveSameLogi[[i]]

  list(
    author=author_i,
    committer=committer_i,
    commitDate=commitDate_i
  ) -> saveEveryThing[[i]]  
}
saveEveryThing
print(saveSameLogi)
saveEveryThing[saveSameLogi] -> saveValidCommitDate
saveValidCommitDate


##?@?޿?
```{r}
isSame <-  vector("logical",length(commitHistory))
for (i in seq_along(commitHistory)){
  isSame[[i]] <- commitHistory[[i]][["commit"]][["author"]][["name"]] == commitHistory[[i]][["commit"]][["committer"]][["name"]]
  b <- commitHistory[isSame]
}
commitdate <- vector("character",length(b))
for (i in seq_along(b)){
  commitdate[[i]] <- b[[i]][["commit"]][["author"]][["date"]]

}
```


```{r}
logiresult <- vector("logical",length(commitHistory))
for (i in seq_along(commitHistory)) {
  logiresult[[i]] <- (commitHistory[[i]]$commit$author$name
        ==commitHistory[[i]]$commit$committer$name)
}
commitDATE <- vector("character",length(commitHistory))
for (i in seq_along(commitHistory)) {
  commitHistory[[i]]$commit$committer$date -> commitDATE[[i]]
}
commitDATE[logiresult] -> commitDatee
commitDatee
```

